### 2019-02-06 sections/relatedwork.tex
additions to related work

>>>>

% NEW RELATED WORK sections

\paragraph{Business process modeling}

A plethora of languages exists to describe, model, display and execute these
processes. YAWL by van der Aalst~\cite{DBLP:journals/is/AalstH05} is one of
these languages. It facilitates modeling and execution of dynamic workflows,
with support for AND, OR and XOR workflow patterns. YAWL programs consist of
Nets, and are therefore programmed visually. BPEL\todo{cite} is another popular business process language.
The standardized language allows for the specification of actions within
business processes, using an XML format. Processes specified in BEPL are
executable, just like YAWL.

\paragraph{IFTTT}

If This Then That (IFTTT)\todo{cite} is a web service that allows users to write and
configure simple conditional statements called applets, that can interact with
web services and IoT devices. These applets can be seen as tiny workflows, that
facilitate collaboration between different services and platforms. The
complexity of the flow is very limited however, and is not geared towards humans
collaborating.

\paragraph{Google forms \& Wufoo}

Google forms\todo{cite} and Wufoo\todo{cite} are web based survey administration apps that allows
users to compose forms and gather data from them. They are comparable to TOP and
iTasks in that they provide an easy way for users to construct forms on the web.
However, Google forms and Wufoo do not allow users to define what the system
then should do with this information, and can therefore not be regarded as a
workflow or business process modeling systems.

\paragraph{Chorus} % (http://www.chorus-home.org/)

Chorus~\cite{chen2017chorus} is a visual programming environment for online
collaboration apps. The goal of Chorus is to allow users to program their own
application, though which a collective task can be coordinated. Users work on a
preset data-type that drives the behavior of the user defined applications.
